Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2022-06-03 analysis/paper/discussion.Rmd
incorporate reviewer comments and resubmit
remove hyphen from citekey

While we are unable to sufficiently address the 
mechanism(s) of starch incorporation with the data obtained in this study, 
the dental calculus model presented here is uniquely suited to explore 
these questions and may improve interpretations of dietary practices in past 
populations. Further analyses using this model can address the call for more 
baseline testing of biases associated with dietary research conducted on dental calculus 
[@lemoyneCalculusPretreatments2021].
Our high-throughput experimental setup allows us a
higher degree of control over the factors that influence starch incorporation and
retention, such as dietary intake, differential survivability of starches, 
and inter- and intra-individual variation in plaque accumulation and mineralisation.
The latter is especially difficult to control *in vivo* as it is influenced by 
numerous factors including genetics, diet, salivary flow, and tooth position and
morphology 
[@jepsenCalculusRemoval2011; @simon-soroOralGeography2013; @proctorSpatialGradient2018; @fagernasMicrobialBiogeography2021; @haffajeeBiofilmPosition2009], 
as well as evolutionary differences [@yatesOralMicrobiome2021].
It can also facilitate training of students and researchers on methods of 
dental calculus analysis, such as starch and phytolith extraction and 
identification, where it can replace the use of finite archaeological resources.

>>>>

While we are unable to sufficiently address the 
mechanism(s) of starch incorporation with the data obtained in this study, 
the dental calculus model presented here is uniquely suited to explore 
these questions and may improve interpretations of dietary practices in past 
populations. Further analyses using this model can address the call for more 
baseline testing of biases associated with dietary research conducted on dental calculus 
[@lemoyneCalculusPretreatments2021].
Our high-throughput experimental setup allows us a
higher degree of control over the factors that influence starch incorporation and
retention, such as dietary intake, differential survivability of starches, 
and inter- and intra-individual variation in plaque accumulation and mineralisation.
The latter is especially difficult to control *in vivo* as it is influenced by 
numerous factors including genetics, diet, salivary flow, and tooth position and
morphology 
[@jepsenCalculusRemoval2011; @simonsoroOralGeography2013; @proctorSpatialGradient2018; @fagernasMicrobialBiogeography2021; @haffajeeBiofilmPosition2009], 
as well as evolutionary differences [@yatesOralMicrobiome2021]. The set of
limitations for our model differ from *in vivo* methods and, as such, we expect
our model to complement the results and interpretations of existing and new
*in vivo* studies.
It can also facilitate training of students and researchers on methods of 
dental calculus analysis, such as starch and phytolith extraction and 
identification, where it can replace the use of finite archaeological resources.
